### 2013-10-28 Doc/MMVR2014/IOSProceedings/results.tex
ADD: proceedings version of the paper
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@610 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

\section{Results} %{{{
\subsection{Aspiration Test}
% As the first step, we evaluate the influence of the Glisson's capsule on the mechanical response of the tissue during
% the aspiration test. 
In~\cite{Hollenstein2006} an \emph{aspiration test} is presented to quantify the local influence of the Glisson's on tissue behaviour.
The aspiration device consists of a tube having 1\,cm in diameter and allows to
control the pressure inside the tube. The test is performed by
attaching the tube to the tissue and measuring the tissue response. We
set up a simulation in SOFA to reproduce the experiment (see
Fig.~\ref{fig-aspiration1}): we meshed a 15$\times$15$\times$15\,mm$^3$ 
cube representing the tissue resulting in 2648 tetrahedra. Then we attached a 1\,cm tube 
and applied a pressure of 3\,kPa inside the tube. The contacts between the tube and tissue sample were modeled using 
an approach based on non-linear complementarity problem presented in~\cite{Duriez2006b} which provides a solution for 
the Signorini's problem while taking into account friction between the objects.
% objects

@@

@@

>>>>

\section{Results} %{{{
\begin{figure}[t]
  \centering
  \includegraphics[height=3.5cm]{figures/aspirationScreenshot.jpg}
  \caption{\label{fig-aspiration1} The SOFA simulation scene of the aspiration test.}
\end{figure}
\subsection{Aspiration Test}
% As the first step, we evaluate the influence of the Glisson's capsule on the mechanical response of the tissue during
% the aspiration test. 
In~\cite{Hollenstein2006} an \emph{aspiration test} is presented to quantify the local influence of the Glisson's on tissue behaviour.
The aspiration device consists of a tube having 1\,cm in diameter and allows to
control the pressure inside the tube. The test is performed by
attaching the tube to the tissue and measuring the tissue response. We
set up a simulation in SOFA to reproduce the experiment (see
Fig.~\ref{fig-aspiration1}): we meshed a 15$\times$15$\times$15\,mm$^3$ 
cube representing the tissue resulting in 2648 tetrahedra. Then we attached a 1\,cm tube 
and applied a pressure of 3\,kPa inside the tube. The contacts between the tube and tissue sample were modeled using 
an approach based on non-linear complementarity problem presented in~\cite{Duriez2006b} which provides a solution for 
the Signorini's problem while taking into account friction between the objects.
% objects

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=7cm]{figures/displacementProfile.pdf}
  \caption{\label{fig-aspiration2} Displacement profile of the cube in the
  aspiration test with (blue) and without (black) the capsule.}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[height=3.5cm]{figures/displacementEvolution.pdf}
  \caption{\label{fig-aspiration3} Evolution of the displacement at the center
  in time for test with (blue) and without (black) the capsule.}
\end{figure}

@@

\begin{figure}[b]
  \centering
  \includegraphics[height=7cm]{figures/modelUnderGravity.png}
  \caption{Liver under gravity with (red) and without (yellow) capsule}
  \label{f:gravity}
\end{figure}
